Title Goes Here

### 2024-05-13 analysis/paper/paper.qmd
plotting EEO word freq

```{r}
ggplot(word_data, aes(x = reorder(word, n), y = n)) +
  geom_col() +
  coord_flip() +  # Flips the axes for easier reading of text
  labs(x = "Words", y = "Frequency", title = "Word Frequency")
```

>>>>

EEO_word %>% 
  filter(n >= 20) %>% 
ggplot() +
  aes(x = reorder(word, n), y = n) +
  geom_col() +
  coord_flip() +  # Flips the axes for easier reading of text
  labs(x = "Words", y = "Frequency", title = "Word Frequency") 
```
